Halo alignments with large scale tidal and velocity fields

### 2013-03-15 paper/main.tex
more text on previous work

\citep{Libeskind2013} %various alignments
\citep{Libeskind2012} %varios alignments

@@

\begin{itemize}
\item
\citep{Zhang2009}
Study the spin and shape alignment against filaments.

@@

They do not see any strong dependance of the environment in the
shape. They do not measure the shape alinment.
\item
\citep{Basilakos2006}
Use a cosmological SPH+N-body simulation to measure the alignment of
cluster halos with their parent supercluster. For both the cluster
halos and parent super-cluster they define the shape via the
non-normalized inertia tensor.  The find that strenght of the
alignments increases with the degree of filamentarity of the
supercluster.

>>>>

@@

\begin{itemize}

\item
\citep{Libeskind2013} %various alignments
Studies shape and spin alignment with the cosmic web defined by the
velocity shear tensor method described in this paper.

The simulation has $2048^3$ particles in a bos of $250$\hMpc,
corresponding to a particles mass of $1.3\times 10^{8}$\hMsun.  Halos
are found using a FOF halo finder with $b=0.17$. The catalog only
include halos more massiven than $3\times 10^{9}$\hMsun.

The shape is defined from the reduced inertia tensor. Results are
reported for three mass bins $M_{\rm vir}<10^{11.5}$\hMsun,
$11^{11.5}<M_{\rm vir}<12^{12.5}\hMsun$ and $M_{\rm vir}>12^{12.5}\hMsun$.

THe identification of the cosmic web is done on a grid of $256^3$ with
a gaussian smoothing of $\sim 1$\hMpc over the velocity field. The
details of this smoothing are different from ours. This is decribed in
detail in the Appendix.

The aligmnet signal of the spin is very weak while the shape alignment
signal is very strong. The alignment is such that the eigenvector
corresponding to the smalles eigenvalue is aligned with the major
axis. This effect is stronger for more massive halos. 
In other words the major axis of a halo is aligned with a filament,
and lies on the plane that define a sheet.

\item
\citep{Trowland2013}

The simulation is the millennium simulation, which has $2160^3$
particles in a volume of $500$\hMpc on a side. This corresponds to a
particle mass of $8.6\times 10^{8}$\hMsun. The catalog uses both halos
and subhalos which were identified with SUBFIND. Only halos with more
than 500 particles were kept to get a robust computation for the spin.

However the analysis are reported ona box of $300$\hMpc on a
side. Four different gaussian smoothing scales are used:

The method to define the filamentary structure is based on the
eigenvalues of the hessian of the density.

\item
\citep{Zhang2009}
Study the spin and shape alignment against filaments.

@@

They do not see any strong dependance of the environment in the
shape. They do not measure the shape alinment.

\item
\citep{Brunino2007}

\item
\citep{Basilakos2006}
Use a cosmological SPH+N-body simulation to measure the alignment of
cluster halos with their parent supercluster. For both the cluster
halos and parent super-cluster they define the shape via the
non-normalized inertia tensor.  The find that strenght of the
alignments increases with the degree of filamentarity of the
supercluster.
